Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-02-22 paper/lostanlenRelevanceScattering.tex
imporved figures

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{figures/baselines}
\caption{Acoustic scene similarity retrieval in the DCASE 2013 private dataset: precisions at rank $k$ ($p@k$) obtained for scattering with or without logarithmic compression, as a function of the rank $k$.
\vl{The x-axis label is wrong. precision should be replaced by "rank $k$". The y-axis should be "precision ($p@k$)". It would be good to have the y-axis range from $0\%$ to $100\%$.
The lines should be thicker and follow a color palette of complementary colors (blue vs. orange). The legends should not be abbreviated: scatT -> scattering, mfcc -> MFCC. } \ja{Should we not have $k$ stricly smaller than $10$ here?} \ml{very true, we should stop at k=9 for all figures. We can see it reaches a plateau. mfcc, early pca should be discarded.}}
\label{fig:ASS_-1}
\end{center}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{figures/log}
\caption{Acoustic scene similarity retrieval in the DCASE 2013 private dataset: precisions at rank $k$ ($p@k$) obtained for scattering with or without logarithmic compression, as a function of the rank $k$.\ml{show only early}}
\label{fig:ASS_0}
\end{center}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{figures/overall}
\caption{Acoustic scene similarity retrieval in the DCASE 2013 private dataset: precisions at rank $k$ ($p@k$) obtained for MFCCs and scattering with logarithmic compression, as a function of the rank $k$.\ml{keep only early approaches, and adapt the text refering to it then.}}
\label{fig:ASS_1}
\end{center}
\end{figure}

>>>>

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{figures/baselines}
\caption{Acoustic scene similarity retrieval in the DCASE 2013 private dataset: precisions at rank $k$ ($p@k$) obtained for scattering with or without logarithmic compression, as a function of the rank $k$.}
\label{fig:ASS_-1}
\end{center}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{figures/log}
\caption{Acoustic scene similarity retrieval in the DCASE 2013 private dataset: precisions at rank $k$ ($p@k$) obtained for scattering with or without logarithmic compression, as a function of the rank $k$.}
\label{fig:ASS_0}
\end{center}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{figures/overall}
\caption{Acoustic scene similarity retrieval in the DCASE 2013 private dataset: precisions at rank $k$ ($p@k$) obtained for MFCCs and scattering with logarithmic compression.}
\label{fig:ASS_1}
\end{center}
\end{figure}
